---
title: "Model Simulation"
output: html_notebook
---
This file is used to run the simulations over our different models in order to estimate the efficency of matching methods.
The matching methods used are:
  * No matching (Benchmark)
  * Coarsened Exact Matching
  * Propensity Matching with Logistic Regression
  * Propensity Matching with Random Forest
  * Cardinality Matching with threshold 0.1
  * Cardinality Matching with threshold 0.01


```{r,, echo=FALSE}
#X11 library is missing: install XQuartz from xquartz.macosforge.org
#install.packages("cem")

library(MASS) #Causal inference
library(Matching) #Causal inference
library(MatchIt) # Causal inference
library(cem) # Coarsened Exact Matching
library(designmatch) #Cardinality Matching
library(randomForest) #Random Forest for propensity score
library(norm) #Norm computation

library(mice) #Data imputation
library(VIM) #Data imputation
library(missMDA) #Data imputation
library(Amelia) #Data imputation

library(ggplot2) #Visualisation
library(scales) #Visualisation
library(grid) #Visualisation
library(RColorBrewer) #Visualisation

source("amputation.R") #To generate missing values
source("plotFunctions.R") #Annex functions used for plotting
source("DataGeneration.R") #To generate dataframe following diven models
source("matchingFunctions.R") #The different matching functions used
source("globalSimulation.R") #To run simulation to compare matching methods
source("missingValSimulation.R") #To run simulation with missing values generated and imputed
```

  
```{r, echo=FALSE}

#We choose here the number of simulation to run (200 simulations ~ 1h)

nombre_simu <- 500

#Uncomment the wanted scenario

#data_scenario_1 <- global_simulation(dataset_1,f_1,nombre_simu)
#data_scenario_2 <- global_simulation(dataset_1,f_2,nombre_simu)
#data_scenario_3 <- global_simulation(dataset_1,f_3,nombre_simu)

#data_scenario_4 <- global_simulation(dataset_2,f_1,nombre_simu)
#data_scenario_5 <- global_simulation(dataset_2,f_2,nombre_simu)
#data_scenario_6 <- global_simulation(dataset_2,f_3,nombre_simu)

#data_scenario_7 <- global_simulation(dataset_3,f_1,nombre_simu)
#data_scenario_8 <- global_simulation(dataset_3,f_2,nombre_simu)
#data_scenario_9 <- global_simulation(dataset_3,f_3,nombre_simu)

# To save the scenario to a file
#saveRDS(data_scenario_1, file = "data_scenario_1.rds")

#  to Restore the object readRDS(file = "my_data.rds")
```


The cell bellow is for similar simulation with missing values generated and imputed in order to assess the robustness of matching methods. 

```{r, echo=FALSE}

#We choose here the number of simulation to run (200 simulations ~ 1h30)

nombre_simu_NA <- 500

#Uncomment the wanted scenario

#data_scenario_NA_1 <- global_simulation_with_NA(dataset_1,f_1,nombre_simu_NA,"MAR","Amelia")
#data_scenario_NA_2 <- global_simulation_with_NA(dataset_1,f_2,nombre_simu_NA,"MAR","Amelia")
#data_scenario_NA_3 <- global_simulation_with_NA(dataset_1,f_3,nombre_simu_NA,"MAR","Amelia")

#data_scenario_NA_4 <- global_simulation_with_NA(dataset_2,f_1,nombre_simu_NA,"MAR","Amelia")
#data_scenario_NA_5 <- global_simulation_with_NA(dataset_2,f_2,nombre_simu_NA,"MAR","Amelia")
#data_scenario_NA_6 <- global_simulation_with_NA(dataset_2,f_3,nombre_simu_NA,"MAR","Amelia")

#data_scenario_NA_7 <- global_simulation_with_NA(dataset_3,f_1,nombre_simu_NA,"MAR","Amelia")
#data_scenario_NA_8 <- global_simulation_with_NA(dataset_3,f_2,nombre_simu_NA,"MAR","Amelia")
#data_scenario_NA_9 <- global_simulation_with_NA(dataset_3,f_3,nombre_simu_NA,"MAR","Amelia")

# To save the scenario to a file
#saveRDS(data_scenario_NA_1, file = "data_scenario__NA_1.rds")
```

We then plot the estimated ATT and the difference in means for each method in order to compare them.
We can also have access to all the results (KS, ratio_var, estimated ATT in order to analyse them)

```{r}
#Balance plotting
#balance_ploting(data_scenario_1)

#ATT plotting
#att_ploting(data_scenario_1)

```


