---
title: "Results of the matching methods on the Traumabase"
output: html_notebook
---

In this notebook, we prepare the traumabse data for imputation and/or inferences.
The call is to use it at the end for matching methods provided in `matchingFunctionsTraumabase`

```{r,, echo=FALSE}

suppressPackageStartupMessages(library(cobalt))#Generate balance tables and plots for covariates of groups preprocessed through matching
suppressPackageStartupMessages(library(ggplot2)) #Visualisation
suppressPackageStartupMessages(library(dplyr))#tool for working with data frame like objects, both in memory and out of memory
suppressPackageStartupMessages(library(reshape2))#Flexibly restructure and aggregate data
suppressPackageStartupMessages(library(tableone))#Create 'Table 1' to Describe Baseline Characteristics

suppressPackageStartupMessages(library(FactoMineR)) # Factorial data analysis
suppressPackageStartupMessages(library(missMDA)) # PCA/MCA with missing values + iterative PC imputation
suppressPackageStartupMessages(library(naniar)) # Missing values exploration and visualization
suppressPackageStartupMessages(library(VIM)) # Missing values exploration and visualization
suppressPackageStartupMessages(library(BaylorEdPsych)) # Little's MCAR test

suppressPackageStartupMessages(library(designmatch)) #Includes functions for the construction of matched samples that are balanced and representative by design
suppressPackageStartupMessages(library(boot)) #Bootstrapping
suppressPackageStartupMessages(library(cem)) #Coarsend Exact Matching
suppressPackageStartupMessages(library(nnet)) #Software for feed-forward neural networks with a single hidden layer, and for multinomial log-linear models.
suppressPackageStartupMessages(library(randomForest)) #Generate Random Forest
suppressPackageStartupMessages(library(Matching)) #Matchign package for propensity


source("matchingFunctionsTraumabase.R") #The different matching functions used

```

Load the data: the traumabase is to be stored in the same file or the correct file should be indicated bellow and above for importing the functions.

```{r, echo=FALSE}
rawData <- read.csv("4_computed_dataset.csv", 
                    na.strings = c("", "NR", "NA", "NF","IMP", "ND"),
                    sep = ",")
```

Based on causal graph (2019-08-29)

```{r, echo=FALSE}
selectedData <- rawData[, c("Numéro.de.centre",
                            "Traitement.anticoagulant",
                            "Traitement.antiagrégants",
                            "Glasgow.initial",
                            "Glasgow.moteur.initial",
                            "Anomalie.pupillaire..Pré.hospitalier.",
                            "Mannitol...SSH",
                            "Régression.mydriase.sous.osmothérapie",
                            "Arrêt.cardio.respiratoire..massage.",
                            "Pression.Artérielle.Systolique..PAS..à.l.arrivée.du.SMUR",
                            "Pression.Artérielle.Diastolique..PAD..à.l.arrivée.du.SMUR",
                            "Fréquence.cardiaque..FC..à.l.arrivée.du.SMUR",
                            "Pression.Artérielle.Systolique..PAS..minimum",
                            "Pression.Artérielle.Diastolique..PAD..minimum",
                            "Fréquence.cardiaque..FC..maximum",
                            "Cristalloïdes",
                            "Colloïdes",
                            "Hémocue.initial",
                            "Delta.Hémocue",
                            "Catécholamines",
                            "SpO2.min",
                            "Délai...arrivée.sur.les.lieux...arrivée.hôpital..",
                            "Score.de.Glasgow.en.phase.hospitalière",
                            "Glasgow.moteur",
                            "Anomalie.pupillaire..Phase.hospitalière.",
                            "FC.en.phase.hospitalière",
                            "Pression.Artérielle.Systolique...PAS",
                            "Pression.Artérielle.Diastolique...PAD",
                            "Doppler.TransCrânien..DTC...Index.de.Pulsatilité..IP..max",
                            "FiO2",
                            "Bloc.dans.les.premières.24h....Neurochirurgie..ex....Craniotomie.ou.DVE.",
                            "Total.Score.IGS",
                            "Température.min",
                            "Acide.tranexamique",
                            "Trauma.crânien..lésion.cérébrale.TDM.",
                            "Osmothérapie",
                            "Pression.intracrânienne..PIC.",
                            "Dérivation.ventriculaire.externe..DVE.",
                            "Craniectomie.dé.compressive",
                            "Décès",
                            "ISS....Head_neck",
                            "ISS....Face",
                            "ISS....External",
                            "Score.ISS")]

colnames(selectedData) <- c("Trauma.center",
                            "Anticoagulant.therapy",
                            "Antiplatelet.therapy",
                            "GCS.init",
                            "GCS.motor.init",
                            "Pupil.anomaly.ph",
                            "Osmotherapy.ph",
                            "Improv.anomaly.osmo",
                            "Cardiac.arrest.ph",
                            "SBP.ph",
                            "DBP.ph",
                            "HR.ph",
                            "SBP.ph.min",
                            "DBP.ph.min",
                            "HR.ph.max",
                            "Cristalloid.volume",
                            "Colloid.volume",
                            "HemoCue.init",
                            "Delta.hemoCue",
                            "Vasopressor.therapy",
                            "SpO2.ph.min",
                            "Medcare.time.ph",
                            "GCS",
                            "GCS.motor",
                            "Pupil.anomaly",
                            "HR",
                            "SBP",
                            "DBP",
                            "TCD.PI.max",
                            "FiO2",
                            "Neurosurgery.day0",
                            "IGS.II",
                            "Temperature.min",
                            "Tranexamic.acid",
                            "TBI",
                            "Osmotherapy",
                            "IICP",
                            "EVD",
                            "Decompressive.craniectomy",
                            "Death",
                            "AIS.head",
                            "AIS.face",
                            "AIS.external",
                            "ISS")
```

Pre-process the data (eliminate erronous cases, recode some covariates)

```{r, echo=FALSE}
##Furthermore, we must recode some of the variables:

recode_NR_by_NA <- function(df, feature_name, to_numeric){
  if (feature_name %in% colnames(df)){
    if (to_numeric){
      df[,feature_name] <- as.numeric(as.character(df[,feature_name]))
    } else {
      df[,feature_name] <- as.factor(df[,feature_name])
    }
  }
  return(df)
}

# Binary and other categorical variables
features_to_recode_1 <- c("Trauma.center",
                          "Anticoagulant.therapy",
                          "Antiplatelet.therapy",
                          "Pupil.anomaly.ph",
                          "Osmotherapy.ph",
                          "Improv.anomaly.osmo",
                          "Cardiac.arrest.ph",
                          "Vasopressor.therapy",
                          "Pupil.anomaly",
                          "Neurosurgery.day0",
                          "Tranexamic.acid",
                          "TBI",
                          "Osmotherapy",
                          "IICP",
                          "EVD",
                          "Decompressive.craniectomy",
                          "Death")

# Numerical variables
features_to_recode_2 <- c("GCS.init",
                          "GCS.motor.init",
                          "SBP.ph",
                          "DBP.ph",
                          "HR.ph",
                          "SBP.ph.min",
                          "DBP.ph.min",
                          "HR.ph.max",
                          "Cristalloid.volume",
                          "Colloid.volume",
                          "HemoCue.init",
                          "Delta.hemoCue",
                          "SpO2.ph.min",
                          "Medcare.time.ph",
                          "GCS",
                          "GCS.motor",
                          "HR",
                          "SBP",
                          "DBP",
                          "TCD.PI.max",
                          "FiO2",
                          "IGS.II",
                          "Temperature.min",
                          "AIS.head",
                          "AIS.face",
                          "AIS.external",
                          "ISS")

for (f in features_to_recode_1){
  selectedData <- recode_NR_by_NA(selectedData,
                                  f,
                                  to_numeric = FALSE)
}

for (f in features_to_recode_2){ 
  selectedData <- recode_NR_by_NA(selectedData,
                                  f,
                                  to_numeric = TRUE)
}
```

Recode levels of Tranexamic.acid, TBI and Death and replace missing values by "0".

```{r, echo=FALSE}
levels(selectedData$Tranexamic.acid) <- c(0, 1)
levels(selectedData$TBI) <- c(0, 1)
levels(selectedData$Death) <- c(0, 1)

levels(selectedData$Neurosurgery.day0) <- c(0, 1)
levels(selectedData$Decompressive.craniectomy)  <- c(0, 1, 0)
levels(selectedData$EVD)  <- c(0, 1, 0)
levels(selectedData$Vasopressor.therapy)  <- c(0, 1, 0)

selectedData$Tranexamic.acid <- sapply(selectedData$Tranexamic.acid,
                                       function(x) dplyr::if_else(is.na(x),
                                                                  0,
                                                                  as.double(as.character(x))))

selectedData$Tranexamic.acid <- as.factor(selectedData$Tranexamic.acid)

selectedData$TBI <- sapply(selectedData$TBI,
                           function(x) dplyr::if_else(is.na(x),
                                                      0,
                                                      as.double(as.character(x))))

selectedData$TBI <- as.factor(selectedData$TBI)

selectedData$Death <- sapply(selectedData$Death, function(x) dplyr::if_else(is.na(x),
                                                                            0,
                                                                            as.double(as.character(x))))
selectedData$Death <- as.factor(selectedData$Death)

selectedData$Neurosurgery.day0 <- sapply(selectedData$Neurosurgery.day0,
                                         function(x) dplyr::if_else(is.na(x),
                                                                    0,
                                                                    as.double(as.character(x))))

selectedData$Neurosurgery.day0 <- as.factor(selectedData$Neurosurgery.day0)
```

Another identified confounder is the ratio of heart frequency (FC) and systolic arterial pressure (PAS) 
and the difference of this index between the first measurements and the arrival at hospital.

```{r, echo=FALSE}
selectedData$Shock.index.ph <- selectedData$HR.ph/selectedData$SBP.ph
selectedData$Shock.index.ph[is.nan(selectedData$Shock.index.ph)] <- 0
selectedData$Shock.index.ph[selectedData$Shock.index.ph==Inf] <- 0


Shock.index <- selectedData$HR/selectedData$SBP
Shock.index[is.nan(Shock.index)] <- 0
Shock.index[Shock.index==Inf] <- 0

selectedData$Delta.shock.index <- selectedData$Shock.index.ph - Shock.index

selectedData <- dplyr::select(selectedData, -c("SBP", "DBP", "HR"))
```

We have a quick look at the variable `Delai...arrivee.sur.les.lieux...arrivee.hopital..` that indicates the time from arrival of the SAMU at the place of the accident to the arrival at the hospital. 

This variable should be given in minutes, but seems to be given in hours by some practitioners. Furthermore there seem to be outliers that might be explained by patients that got retransfered from one hospital to another one. Hence the range of observed values is fairly large, even if we drop the outliers.

```{r, echo=FALSE}
summary(selectedData$Medcare.time.ph)

d1 = density(selectedData[which((selectedData$TBI %in% c("1")| selectedData$AIS.head>=2) & (!is.na(selectedData$Medcare.time.ph))), "Medcare.time.ph"])

plot(d1, col="red", 
     main = "Observed Temps.lieux.hop for patients with trauma cranien or AIS.tete >=2", 
     cex.main = 0.65)

hist(selectedData[which((selectedData$TBI %in% c("1")| selectedData$AIS.head>=2) & (!is.na(selectedData$Medcare.time.ph))), "Medcare.time.ph"],
     col=rgb(1,0,0,0.5),
     main="Medcare.time.ph", 
     xlab="Time (in hours or minutes)",
     breaks = 25)
```

Let's have a closer look at patients with `Medcare.time.ph` < 20.

```{r, echo=FALSE}
hist(selectedData[which((selectedData$TBI %in% c("1")| selectedData$AIS.head>=2) & (!is.na(selectedData$Medcare.time.ph)) &
selectedData$Medcare.time.ph < 20), "Medcare.time.ph"],
     col=rgb(1,0,0,0.5),
     main=paste0("Medcare.time.ph (total # of TBI patients with observed Time: ",
                 sum((selectedData$TBI %in% c("1")| selectedData$AIS.head>=2) & (!is.na(selectedData$Medcare.time.ph)), na.rm=T) ,")"),
     xlab="Time (in hours or minutes)",
     breaks = 25)
```

Exploring and visualizing missing values

On entire sample
Let's see how many missing values we have for each variable as for now:

```{r, echo=FALSE}
null.data <- sapply(selectedData, function(x) sum(is.na(x)))

dims <- dim(selectedData)
variable.names <- colnames(selectedData)
missing.data <- as.data.frame(cbind(variable.names, null.data),
                              stringsAsFactors = FALSE)

missing.data[-1] <- apply(missing.data[-1], 1:2, function(x) as.numeric(as.character(x)))
rownames(missing.data) <- NULL

missing.data.reshaped <- data.table::melt(missing.data,
                                          id.var="variable.names")

ggplot(missing.data.reshaped, aes(x = reorder(variable.names, value), y = (100 * value / dims[1]), fill = variable)) + 
  geom_bar(stat = "identity") + theme(axis.text.x= element_text(angle=65,hjust=1, size=6)) + xlab("Variable") + ylab("Percentage") + ggtitle("Percentage of missing values")
```

We also make these assumptions: When there are missing values for any of these procedures done in the hospital, they are assumed not to have been done (as per the doctors' recommendation): 

```{r, echo=FALSE}
recode_NoTrauma <- function(f, feature_name){
  if (feature_name %in% colnames(f)){
    if (feature_name == "Osmotherapy"){
      f[is.na(f[,feature_name]),feature_name] <- "Rien"
      return(f)
    }
    else if (feature_name == "Improv.anomaly.osmo"){
      f[is.na(f[,feature_name]),feature_name] <- "Non testé"
      return(f)
    }
    else{
      f[is.na(f[,feature_name]),feature_name] <- 0
      return(f)
    }
  }
  return(f)
}

features_to_recode_3 <- c("Vasopressor.therapy",
                          "Osmotherapy",
                          "EVD",
                          "Decompressive.craniectomy",
                          "Neurosurgery.day0",
                          "Improv.anomaly.osmo")

for (i in features_to_recode_3){
  selectedData <- recode_NoTrauma(selectedData, i)
}
```

Why can't we do the same for `TCD.PI.max`? Because, even though the "NA" entries probably mean these values were not measured/monitorized, there was still a real actual value inerent to the patient for these variables that we can't access and might have impacted their health. 
This is a choice we make to deal with variables that are in $\mathbb{R}\times NA$ buy that are in fact mixed variables of quantitative and categorical values. Other choices of dealing with this problem need to be investigated.__


These changes have a sizable impact on the number of missing data entries:

```{r, echo=FALSE}
null.data <- sapply(selectedData,
                    function(x) sum(is.na(x)))

dims<- dim(selectedData)
variable.names <- colnames(selectedData)
missing.data <- as.data.frame(cbind(variable.names, null.data),
                              stringsAsFactors = FALSE)
missing.data[-1] <- apply(missing.data[-1], 1:2,
                          function(x) as.numeric(as.character(x)))
rownames(missing.data) <- NULL

missing.data.reshaped <- melt(missing.data, id.var="variable.names")

ggplot(missing.data.reshaped, aes(x = reorder(variable.names, value), y = (100 * value / dims[1]), fill = variable)) + 
  geom_bar(stat = "identity") + theme(axis.text.x= element_text(angle=65,hjust=1, size=6)) + xlab("Variable") + ylab("Percentage") + 
  ggtitle("Percentage of missing values")
```

# On target group of TBI patients

Our causal inference analysis will only focus on the patients that have had a lesion visible on the CT scan (tranlated into Trauma.cranien == 1) and/or an AIS.tete score equal or higher than 2, given that the aim of our study is to analyse the (causal) effect of the administration of tranexamic acid in patients that have a brain injury. We should examine the missing values (pattern) specifically on this subset of patients and impose a lower threshold for the % of missing values allowed for each variable.

For the patients we will choose to run causal inference (`Trauma.cranien == 1` and/or `AIS.tete => 2`), let's see how many __pre-treatment variables__ are missing:

```{r, echo=FALSE}
pretreatment <- c("Trauma.center",
                  "Anticoagulant.therapy",
                  "Antiplatelet.therapy",
                  "GCS.init",
                  "GCS.motor.init",
                  "Pupil.anomaly.ph",
                  "Osmotherapy.ph",
                  "Improv.anomaly.osmo",
                  "Cardiac.arrest.ph",
                  "SBP.ph",
                  "DBP.ph",
                  "HR.ph",
                  "SBP.ph.min",
                  "DBP.ph.min",
                  "HR.ph.max",
                  "Shock.index.ph", 
                  "Delta.shock.index",
                  "Cristalloid.volume",
                  "Colloid.volume",
                  "HemoCue.init",
                  "Delta.hemoCue",
                  "Vasopressor.therapy",
                  "SpO2.ph.min",
                  "Medcare.time.ph",
                  "GCS",
                  "GCS.motor",
                  "Pupil.anomaly",
                  "HR",
                  "SBP",
                  "DBP",
                  "SpO2",
                  "IGS.II",
                  "TBI",
                  "AIS.head",
                  "AIS.face",
                  "AIS.external",
                  "ISS")


pretreatment <- intersect(pretreatment, colnames(selectedData))

missing.in.pretreatment <- vector(mode = "numeric", length = length(pretreatment))

for (i in 1:length(pretreatment)){
  missing.in.pretreatment[i] <- length(selectedData[((selectedData$TBI %in% c("1")) |(selectedData$AIS.head >= 2)) & is.na(selectedData[,pretreatment[i]]),colnames(selectedData) %in% pretreatment[i]])/length((selectedData[(selectedData$TBI %in% c("1"))|(selectedData$AIS.head >= 2),colnames(selectedData) %in% pretreatment[i]]))
}

a <- barplot(missing.in.pretreatment*100, cex.names = 0.5, names.arg="",ylab = "Percentage of missing values", main = "% of missing values for treatment variables in patients w/ trauma cranien or AIS.tete >= 2", las = 2, cex.main = 0.8, cex.lab = 0.8)
text(a[,1], -3.7, srt = 60, adj= 1, xpd = TRUE, labels = pretreatment, cex=0.4)
```

None of these variables seem to be missing enough to justify their elimination, especially considering that the doctors have selected the ones that are missing the most as important cofounders: Alcool, Lactates, pCO2, paO2 and temps.lieux.hop. 


Now, for the patients we will use to run causal inference (`Trauma cranien == 1` and/or `AIS.tete => 2`), let's see how many __treatment variables__ are missing:

```{r, echo=FALSE}
treatments <- c("Osmotherapy.ph",
"Cristalloid.volume",
"Colloid.volume",
"Vasopressor.therapy",
"FiO2",
"Neurosurgery.day0",
"Tranexamic.acid",
"Osmotherapy",
"EVD",
"Decompressive.craniectomy") 


treatments <- intersect(treatments, colnames(selectedData))

missing.in.treatment <- vector(mode = "numeric",
                               length = length(treatments))

for (i in 1:length(treatments)){
  missing.in.treatment[i] <- length(selectedData[((selectedData$TBI %in% c("1")) |(selectedData$AIS.head >= 2)) & is.na(selectedData[,treatments[i]]),colnames(selectedData) %in% treatments[i]])/length((selectedData[(selectedData$TBI %in% c("1"))| (selectedData$AIS.head >= 2),colnames(selectedData) %in% treatments[i]]))
}

a <- barplot(missing.in.treatment*100, cex.names = 0.5, names.arg="",ylab = "Percentage of missing values", main = "% of missing values for treatment variables in patients w/ trauma cranien or AIS.tete >= 2", las = 2, cex.main = 0.8, cex.lab = 0.8, ylim = c(0,50))
text(a[,1], -3.7, srt = 30, adj= 1, xpd = TRUE, labels = treatments, cex=0.5)
```

The variables `Catecholamines`, `KTV.poses.avant.TDM`, `Dose.NAD.depart`, `Osmotherapie`, `PIC`, `DVE`, `Hypothermie.therapeutique`, `Craniectomie.decompressive` and `Acide.tranexamique` do not have any missing values at this point given our previous assumptions. 

`DTC.IP.max` has a concerning number of missing entries, especially considering it's potential impact on the results of the causal inference analysis - however the doctors considered it as a very important variable so we shall not delete it. Let's look out for how its distribution changes after the imputation of missing data.

```{r, echo=FALSE}
df <- selectedData %>%
        filter((TBI %in% c("1")) | (AIS.head >= 2)) %>%
        dplyr::select(c("TCD.PI.max","Trauma.center")) %>%
        mutate(is.missing = is.na(TCD.PI.max)) %>%
        group_by(Trauma.center) %>%
        summarise(missing.DTC = mean(is.missing), n = n()) %>%
        mutate(effectifs = paste(n, "TBI \n patients"))
        

ggplot(df, aes(x = Trauma.center)) +
  geom_col(aes( y = missing.DTC*100)) +
  geom_text(aes(y = missing.DTC*100, label = effectifs),
            fontface = "bold", vjust = 1.4, color = "black", size = 4) +
  ylab("% missing DTC.IP.max") + 
  xlab("Trauma Center") +
  labs(fill = "Number of\nTBI patients") +
  theme(axis.text.x= element_text(angle=65,hjust=1, size=12))
```

Now we prepare the datasets to perform the causal analyses on:

```{r, echo=FALSE}
data_indAll <- selectedData 

data_indTBI <- data_indAll %>%
                  filter(TBI==1 | AIS.head >= 2)

index_indTBI <- which(data_indAll$TBI == 1 | data_indAll$AIS.head >= 2)


# Data selection and MDA
levels(data_indAll$Anticoagulant.therapy)<- c(0, 1)
levels(data_indAll$Antiplatelet.therapy)<- c(0, 1)
levels(data_indAll$Osmotherapy.ph)<- c(0, 1, 2, 3, 4, 5)
levels(data_indAll$Pupil.anomaly.ph)<- c(0, 1, 2, 3)
levels(data_indAll$Improv.anomaly.osmo)<- c(0, 1, 2)
levels(data_indAll$Cardiac.arrest.ph)<- c(0, 1)
levels(data_indAll$Pupil.anomaly)<- c(0, 1, 2)
levels(data_indAll$Osmotherapy)<- c(0, 1, 2)
levels(data_indAll$IICP)<- c(0, 1, 2, 3)
levels(data_indAll$Osmotherapy)<- c(0, 1, 2)

data_indAll_selected <- dplyr::select(data_indAll,"Trauma.center",
"Cardiac.arrest.ph",
"SBP.ph",
"DBP.ph",
"HR.ph",
"SBP.ph.min",
"DBP.ph.min",
"HR.ph.max",
"Cristalloid.volume",
"Colloid.volume",
"HemoCue.init",
"Delta.hemoCue",
"Vasopressor.therapy",
"SpO2.ph.min",
"AIS.external",
"Shock.index.ph",
"Delta.shock.index")


data_study_var <- c("Trauma.center",
"Cardiac.arrest.ph",
"SBP.ph",
"DBP.ph",
"HR.ph",
"SBP.ph.min",
"DBP.ph.min",
"HR.ph.max",
"Cristalloid.volume",
"Colloid.volume",
"HemoCue.init",
"Delta.hemoCue",
"Vasopressor.therapy",
"SpO2.ph.min",
"AIS.external",
"Shock.index.ph",
"Delta.shock.index") 

data_study <- intersect(data_study_var, colnames(selectedData))

missing.in.data <- vector(mode = "numeric", length = length(data_study))

for (i in 1:length(data_study)){
  missing.in.data[i] <- length(selectedData[is.na(selectedData[,data_study[i]]),
                                            colnames(selectedData) %in% data_study[i]])/length((selectedData[,colnames(selectedData) %in% data_study[i]]))
}

a <- barplot(missing.in.data*100, cex.names = 0.5, names.arg="",
             ylab = "Percentage of missing values",
             main = "% of missing values for cofounders in patients",
             las = 2, cex.main = 0.8, cex.lab = 0.8, ylim=c(0,40))
text(a[,1], -3.7, srt = 60, adj= 1, xpd = TRUE, labels = data_study_var, cex=0.4)
grid(0,4,lty=2,lwd=1)
```

PCA: function FAMD of FactoMineR to realize a PCA on mixte data

```{r, echo=FALSE}

res_impute <- imputeFAMD(data_indAll_selected)
res_famd <- FAMD(data_indAll_selected, tab.comp=res_impute$tab.disj, ncp=26)

# select TBI patients
res_famd_sliced <- res_famd$ind$coord[index_indTBI,]
Traumabase <- cbind.data.frame(res_famd_sliced, data_indTBI$Tranexamic.acid)
Traumabase <- cbind.data.frame(Traumabase, data_indTBI$Death)
colnames(Traumabase)[27] <- "treat"
colnames(Traumabase)[28] <- "Y"

## groups of patients

# GroupPatients <- yaml::read_yaml("head_traumas_classification.yml") #Group Patients
# group_id <- rawData[, c("ISS....Selection")]
# group_id_sliced <- group_id[index_indTBI]
# res_group <- cbind.data.frame(res_vf, group_id_sliced)
# colnames(res_group)[29] <- "group"
# 
# group_axonale_diffuse <- which(res_group$group %in% GroupPatients$classes$`Lésion axonale diffuse`)
# group_extra_axiale <- which(res_group$group %in% GroupPatients$classes$`Lésion extra-axiale`)
# group_intra_axiale <- which(res_group$group %in% GroupPatients$classes$`Lésion intra-axiale`)
# group_grades_low <- which(res_group$group %in% GroupPatients$grades$Low)
# group_grades_high <- which(res_group$group %in% GroupPatients$grades$High)


```


# Propensity score, cardinality and coarsened matching function for bootstrapping (returns the ATT)
```{r, echo=FALSE}
bootstrapping_Traumabase <- function (dataset, matching_function, nombre_simu){
  cpy_dataset <- dataset
  return (boot(cpy_dataset, statistic=matching_function, R=nombre_simu))
}

prop_rf_match_boot_res <- boot.ci(bootstrapping_Traumabase(Traumabase,matching_prop_rf_bootstrap,10),type="basic")
prop_logit_match_boot_res <- boot.ci(bootstrapping_Traumabase(Traumabase,matching_prop_logit_bootstrap,10),type="basic")
cem_match_boot_res <- boot.ci(bootstrapping_Traumabase(Traumabase,matching_cem_bootstrap,10),type="basic")
card_match_boot_res <- boot.ci(bootstrapping_Traumabase(Traumabase,matching_card_bootstrap,10),type="basic")

```

```{r, echo=FALSE}
#plot covariate balance propensity with logit before and after matching
love.plot(x = balMatch,stat = c("mean.diffs", "variance.ratios"), stars="none" ,threshold = c(m = 0.1, v = 1.2), abs = TRUE)

#plot covariate balance propensity with RF before and after matching

love.plot(x = balMatchRF,stat = c("mean.diffs", "variance.ratios"), stars="none" ,threshold = c(m = 0.1, v = 1.2), abs = TRUE)


```

```{r, echo=FALSE}
#Plot balance Y an pscore

bal.plot(obj = Match.out_log, formula = treat ~ Y ,
         data = dataset,
         var.name = "Y",
         which = "both")


bal.plot(obj = Match.out_log, formula = treat ~ pscore ,
         data = dataset,
         var.name = "pscore",
         which = "both")
  


bal.plot(obj = Match.outRF, formula = treat ~ Y ,
         data = dataset,
         var.name = "Y",
         which = "both")

bal.plot(obj = Match.outRF, formula = treat ~ pscore ,
         data = dataset,
         var.name = "pscore",
         which = "both")
  
  
```

Dataset complexity traumabase

```{r, echo=FALSE}

#Diff in means

plot(abs(mean1-mean2),main="Diff in means",xlab="Dim",col = c("slateblue", "skyblue"),pch=19)
abline(coef = c(1, 0), col = 2)
abline(coef = c(0.5, 0), col = 3)

#VarianceRatio

plot(Var1/Var2,main="Var Ratio",col = c("slateblue", "skyblue"),pch=19,xlab="Dim")
abline(coef = c(1, 0), col = 2)
abline(coef = c(2, 0), col = 3)

```

